A Logical Solution of the Linearity Challenge

### 2025-01-16 paper/main.lagda.tex
basic setup, language syntax and semantics

%\usepackage{graphicx}%
%\usepackage{multirow}%
\usepackage{amsmath,amssymb,amsfonts}%
\usepackage{amsthm}%
\usepackage{mathrsfs}%
\usepackage[title]{appendix}%
\usepackage{xcolor}%
\usepackage{textcomp}%
\usepackage{manyfoot}%
%\usepackage{booktabs}%
%\usepackage{algorithm}%
%\usepackage{algorithmicx}%
%\usepackage{algpseudocode}%
\usepackage{listings}%
%%%%

@@

\title{A Simple Formalization of CP}

@@

\section{Introduction}\label{sec1}

The Introduction section, of referenced text \cite{bib1} expands on the background of the work (some overlap with the Abstract is acceptable). The introduction should not include subheadings.

>>>>

%\usepackage{graphicx}%
%\usepackage{multirow}%
\usepackage{amsmath,amssymb,amsfonts}%
\usepackage{amsthm}%
\usepackage{mathrsfs}%
\usepackage[title]{appendix}%
\usepackage{xcolor}%
\usepackage{textcomp}%
\usepackage{manyfoot}%
%\usepackage{booktabs}%
%\usepackage{algorithm}%
%\usepackage{algorithmicx}%
%\usepackage{algpseudocode}%
\usepackage{listings}%
\usepackage{agda}
\usepackage{xspace}
%%%%
\input{macros}

@@

\title{A Logical Solution of the Linearity Challenge}

@@

\section{Introduction}
\label{sec:introduction}

\section{Language}

\[
    \begin{array}[t]{rcll}
        P, Q & ::= & \Link\x\y \\
            & | & \Close\x \\
            & | & \Fail\x \\
            & | & \Wait\x.P \\
            & | & \Select\x{\InTag_i}\z.P \\
            & | & \Case\x\z{P}{Q} \\
            & | & \Fork\x\y\z{P}{Q} \\
            & | & \Join\x\y\z.P \\
            & | & \Cut\x{P}{Q} \\
    \end{array}
\]

\[
    \begin{array}{rrcll}
      \SLink &
      \Link\x\y & \pcong & \Link\y\x \\
      \SComm &
      \Cut\x{P}{Q} & \pcong & \Cut\x{Q}{P} \\
      \SWait &
      \Cut\x{\Wait\y.P}{Q} & \pcong & \Wait\y.\Cut\x{P}{Q} & x \ne y \\
      \SFail &
      \Cut\x{\Fail\y}{P} & \pcong & \Fail\y & x \ne y \\
      \SSelect &
      \Cut\x{\Select\y{\InTag_i}\z.P}{Q} & \pcong & \Select\y{\InTag_i}\z.\Cut\x{P}{Q} & x \ne y,z \\
      \SCase &
      \Cut\x{\Case\y\z{P}{Q}}{R} & \pcong & \Case\y\z{\Cut\x{P}{R}}{\Cut\x{Q}{R}} & x \ne y,z \\
      \SForkL &
      \Cut\x{\Fork\y\u\v{P}{Q}}{R} & \pcong & \Fork\y\u\v{\Cut\x{P}{R}}{Q} & x \in \fn{P}\setminus\set{y,u,v} \\
      \SForkR &
      \Cut\x{\Fork\y\u\v{P}{Q}}{R} & \pcong & \Fork\y\u\v{P}{\Cut\x{Q}{R}} & x \in \fn{Q}\setminus\set{y,u,v} \\
      \SJoin &
      \Cut\x{\Join\y\u\v.P}{Q} & \pcong & \Join\y\u\v.\Cut\x{P}{Q} & x \ne y,u,v \\
      \\
      \RLink &
      \Cut\x{\Link\x\y}{P} & \red & P\subst\y\x \\
      \RFail &
      \Cut\x{\Fail\y}{P} & \red & \Fail\y & x \ne y \\
      \RClose &
      \Cut\x{\Close\x}{\Wait\x.P} & \red & P \\
      \RSelect &
      \Cut\x{\Select\x{\Tag_i}\y.P}{\Case\x\y{Q_1}{Q_2}} & \red & \Cut\y{P}{Q_i} & i\in\set{1,2} \\
      \RFork &
      \Cut\x{\Fork\x\y\z{P}{Q}}{\Join\x\y\z.R} & \red & \Cut\y{P}{\Cut\z{Q}{R}} \\
      \RCut &
      \Cut\x{P}{R} & \red & \Cut\x{Q}{R} & P \red Q \\
      \RCong &
      P & \red & Q & P \pcong R \red Q \\
    \end{array}
\]

Introduction section, of referenced text \cite{bib1} expands on the background of the work (some overlap with the Abstract is acceptable). The introduction should not include subheadings.
